A family of accessibility measures (bringing balance back?)

### 2025-01-03 paper/manuscript.qmd
Added the TRB presentation

<!-- 
## next steps
- grocery stores for example; maybe 2 grids?
- bibliometric analysis 
- - draft of this end of jan 2025

>>>>

<!-- 
## QUESTIONS:
- what does k=1 mean? What does assuming k=1, so the units can be kept mean for the model? Is it meaningless?
- not sure if the singly-constrained (PRODUCTION case) makes sense.. It sort of does..? I believe this needs to be figured out before the doubly constrained case. Pi needs to be integrated somehow. 
- doubly constrained still needs to be solved.

## next steps
- grocery stores for example; maybe 2 grids?
- bibliometric analysis 
- - draft of this end of jan 2025
